manuscript_figures

### 2024-06-03 scripts/manuscript_figures.Rmd
maade map panels a and b

# Convert sites dataframe to an sf object with CRS 4326
sites_sf <- st_as_sf(sites, coords = c("Longitude", "Latitude"), crs = 4326)

# Get Rhode Island state boundaries and set CRS to 4326
ri_state <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>%
  filter(ID == "rhode island")

# Define your rectangle sizes (adjust as needed)
rect_size1 <- 0.01 # Smaller rectangle
rect_size2 <- 0.02 # Larger rectangle

@@

# Apply the create_rectangle function to each site for both rectangle sizes
site_rectangles <- lapply(st_geometry(sites_sf), function(site) {
  rectangle1 <- create_rectangle(site, rect_size1)
  rectangle2 <- create_rectangle(site, rect_size2)
  list(rectangle1, rectangle2)
})

# Combine all rectangles into one sf object
site_rectangles <- do.call(rbind, unlist(site_rectangles, recursive = FALSE))

# Set CRS for combined rectangles
st_crs(site_rectangles) <- st_crs(sites_sf)

# Plot
panelA <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_sf(data = site_rectangles, color = "red2", fill = NA, size = 1) + # Add rectangles around sites
  geom_sf(data = sites_sf, color = "blue", size = 3) + # Add site points for reference
  coord_sf(xlim = c(-72, -71.0), ylim = c(41.1, 42.1), expand = FALSE) + # Zoom level
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.1, "in"), pad_y = unit(0.4, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme_classic() # Remove axes and background

panelA
```

>>>>

# Convert sites dataframe to an sf object
sites_sf <- st_as_sf(sites, coords = c("Longitude", "Latitude"), crs = 4326)

# Get Rhode Island state boundaries
ri_state <- states(cb = TRUE) %>% 
  filter(STUSPS == "RI") %>%
  st_transform(crs = 4326)

# Define the larger rectangle size (adjust as needed)
rect_size <- 0.02

@@

# Apply the create_rectangle function to each site
site_rectangles <- lapply(st_geometry(sites_sf), function(site) {
  create_rectangle(site, rect_size)
})

# Combine all rectangles into one sf object
site_rectangles <- do.call(rbind, site_rectangles)
st_crs(site_rectangles) <- st_crs(sites_sf) # Ensure CRS is set for combined rectangles

# Define label data
labels <- data.frame(
  name = c("Narragansett\nBay", "Atlantic\nOcean"),
  lat = c(41.6, 41.3),
  lon = c(-71.35, -71.2)
)

# Plot
panelA <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_sf(data = site_rectangles, color = "red2", fill = NA, size = 2) + # Add rectangles around sites
  #geom_sf(data = sites_sf, color = "blue", size = 3) + # Add site points for reference
  geom_text(data = labels, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  coord_sf(xlim = c(-72, -71.0), ylim = c(41.1, 42.1), expand = FALSE) + # Zoom level
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.1, "in"), pad_y = unit(0.4, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme_classic() # Remove axes and background

panelA

# Save the plot to a file
ggsave("output/figures/figure_1A.png", plot = panelA, width = 8, height = 6)

# Filter transect data by site
transect_fw <- filter(site, Site == "Fort Wetherill")

# Define label data
labels <- data.frame(
  name = c("Fort\nWetherill"),
  lat = c(41.485),
  lon = c(-71.368)
)

# Plot
panelB <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_point(data = transect_fw,
             aes(x = Start.Longitude, y = Start.Latitude),
            color = "red", size = 3) + # Add start points of transects
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.5, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering) +
    geom_text(data = labels, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  theme_classic() + # Remove axes and background
  xlim(c(-71.45, -71.3)) + # Set longitude range
  ylim(c(41.42, 41.5))   # Set latitude range

panelB

# Save the plot to a file
ggsave("output/figures/figure_1B.png", plot = panelB, width = 8, height = 6)
